### 2019-07-18 manuscript/abstract.tex
All co-authors input added, figures corrected

If particular traits consistently affect rates of speciation and extinction, broad macroevolutionary patterns can be understood as consequences of selection at high levels of the biological hierarchy.
Identifying traits associated with diversification rate differences is complicated by the wide variety of characters under consideration and the statistical challenges of testing for associations from comparative phylogenetic data.
Ploidy (diploid \vs polyploid states) and breeding system (self-incompatible \vs self-compatible states) have been repeatedly suggested as possible drivers of differential diversification.
We investigate the connections of these traits, including their interaction, to speciation and extinction rates in Solanaceae.
We show that the effect of ploidy on diversification can be largely explained by its correlation with breeding system and that additional unknown factors, alongside breeding system, determine diversification rates.
These results are largely robust to allowing for diploidization.
Finally, we find that the most common evolutionary pathway to polyploidy in Solanaceae occurs via direct breakdown of self-incompatibility by whole genome duplication, rather than indirectly via breakdown followed by polyploidization.

>>>>

If particular traits consistently affect rates of speciation and extinction, broad macroevolutionary patterns can be understood as consequences of selection at high levels of the biological hierarchy.
Identifying traits associated with diversification rate differences is complicated by the wide variety of characters under consideration and the statistical challenges of testing for associations from comparative phylogenetic data.
Ploidy (diploid \vs polyploid states) and breeding system (self-incompatible \vs self-compatible states) have been repeatedly suggested as possible drivers of differential diversification.
We investigate the connections of these traits, including their interaction, to speciation and extinction rates in Solanaceae.
We show that the effect of ploidy on diversification can be largely explained by its correlation with breeding system and that additional unknown factors, alongside breeding system, influence diversification rates.
These results are largely robust to allowing for diploidization.
Finally, we find that the most common evolutionary pathway to polyploidy in Solanaceae occurs via direct breakdown of self-incompatibility by whole genome duplication, rather than indirectly via breakdown followed by polyploidization.

### 2019-07-18 manuscript/discussion.tex
All co-authors input added, figures corrected

%B:  at least two surprising outcomes: (1)  D and P on background of C, and (2) SC not as dead of an end as it was in goldberg2010, if P is partitioned out (can be framed as kind of path-dependence, i.e. qIC path different than rho path, or same as (1), so that I and C are less different on the background of D.
%
Species are composed of vast assemblages of variable traits.
Many traits are both heritable and possibly affect the propensity of species to perish or multiply \citep{lewontin_1970}.
%B: I subtly altered the previously second sentence and split into two, to link heritable traits with those that affect diversification. The implication was not clear---"many are heritable and many affect fitness" is not necessarily that some traits fall under both categories.
%was: Species are composed of vast assemblages of variable traits, many traits are heritable, and many traits could affect the propensity of species to perish or multiply \citep{lewontin_1970}.
Examining the effects of complex trait combinations on lineage diversification, however, remains challenging.
%
Focusing first on ploidy and then on breeding system, we found that considering each trait in isolation provides an incomplete story.
Considering them together, and in conjunction with another hidden factor, provides a fuller picture of macroevolutionary dynamics within Solanaceae.
We hope our work serves as an example of how phylogenetic comparative methods can be used to disentangle the contributions of interacting traits to heterogeneous lineage diversification, and how to statistically argue for increasing complexity in diversification modeling.

@@

%R- let's not get into the weeds of what is a hidden state (I remove the use of trait  for state because a state is what the model receives). Jeremy does a good job discussing this in his paper so no need.
%     but don't be circular, test in different clade
% alpha is always low: new supp fig showing how A & B are inferred on the tree?  at least for ID/CD/CP+A/B model - it is low because not enough transitions and mostly a different process towards the tips-who knows what is happening there?
%Here Rosana adds the value of adding traits with the lumped models
As more trait information becomes available for macroevolutionary studies, it is important not only recognizing the role of hidden states as a part of a general modeling approach, but also questioning whether adding more traits to diversification studies is relevant.
More generally, when analyzing the value of adding additional traits to an already complex model with or without hidden states, we find that using lumped models  is a key tool to verify that adding a trait improves our understanding of the diversification patterns (\cref{figure:lumped,table:lumped}).
%R-removed this: %In our analyses, we find that the transition rates between and within hidden traits did not affect the direction of the net diversification differences. 
%We find that it is important to allow for the hidden state transition rates to be asymmetrical, because those models tend to provide a better fit than models that fix the hidden state transition rates to be equal (\cref{suppfigure:asymmetric,supptable:asymmetry}).

Although we fit an extensive set of models in order to relax a variety of assumptions, we did not explore the process of trait change in conjunction with speciation.
That is, our models all assume anagenetic trait evolution and ignore cladogenetic shifts.
Anagenetic and cladogenetic changes can be separated with phylogenetic models \citep{mayrose_2011, goldberg_2012, magnuson-ford_2012}. 
These have been previously applied to estimate the relative contribution of anagenetic and cladogenetic shifts in breeding system \citep{goldberg_2012} and polyploidization \citep{zhan_2016, freyman_2017}.
We did not explore cladogenetic trait change because of the vast increase in parameter space and model number, outside the scope of our already complex and extensive modeling framework. %IM: #29
Although \citet{goldberg_2012} found that allowing cladogenetic changes did not substantially affect inference of net diversification rates associated with breeding system, future work could test whether this process affects diversification rate estimates with the more complex state and parameter spaces of our other models.

@@

With evolution predominantly in the direction from diploid to polyploid, and from SI to SC, surviving lineages will tend to become SC polyploids.
We find that in Solanaceae, the pathway to this state is more likely to consist of a single step ($ID \rightarrow CP$) than two steps ($ID \rightarrow CD \rightarrow CP$; \cref{figure:pathways}).
Although this question focuses on the process of state transitions, we also show that its answer is affected by the process of lineage diversification.
We used a simple mathematical approach to investigate the contributions of the two pathways, but future work could instead rely on stochastic character mapping to more directly estimate the numbers of each type of transition.

@@

Our findings prompt several further questions about the macroevolutionary pathways of ploidy and breeding system.
%
First, our support for the direct pathway is consistent with the idea that breakdown of SI by whole genome duplication---via diploid `heteroallelic' pollen---may often trigger the evolution of gender dimorphism as a different mechanism of inbreeding avoidance \citep{miller_2000}.
A further test of this hypothesis would additionally examine the propensity of polyploids generated through either pathway to become dioecious \citep{robertson_2011}.
Second, we might wonder whether the propensity for a polyploid species to diversify depends on whether it arose via the one-step or two-step pathway.
This could be tested with a different form of a hidden state model, in which the polyploid state is subdivided into parts, reflecting the arriving path taken to that state. %IM: #30
Such an estimate of path-dependence could also include the possibility of different diversification rates for the subdivided $CP$ substates.
Third, the generality of our findings in other families remains to be assessed.
An identical procedure could be used in other families with gametophytic SI.
In clades with sporophytic SI systems, however, SI is not disabled by whole genome duplication, so there is no one-step pathway \citep{miller_2000,mable_2004}.
The correlation between breeding system and ploidy may therefore be different in sporophytic systems, and it is unclear whether one of the two-step pathways might predominate.
% pathways: compare/contrast with robertson2011
%     \rho_I > \rho_C in all!
%     likely way to lose SI
%     likely way to become P

>>>>

%B:  at least two surprising outcomes: (1)  D and P on background of C, and (2) SC not as dead of an end as it was in goldberg2010, if P is partitioned out (can be framed as kind of path-dependence, i.e. qIC path different than rho path, or same as (1), so that I and C are less different on the background of D.
%
Species are composed of vast assemblages of variable traits.
Many traits are both heritable and possibly affect the propensity of species to perish or multiply \citep{lewontin_1970}.
%B: I subtly altered the previously second sentence and split into two, to link heritable traits with those that affect diversification. The implication was not clear---"many are heritable and many affect fitness" is not necessarily that some traits fall under both categories.
%was: Species are composed of vast assemblages of variable traits, many traits are heritable, and many traits could affect the propensity of species to perish or multiply \citep{lewontin_1970}.
Examining the effects of complex trait combinations on lineage diversification, however, remains challenging.
%
Focusing first on ploidy and then on breeding system, we found that considering each trait in isolation provides an incomplete story.
Considering them together, and in conjunction with another hidden factor, provides a more complete picture of macroevolutionary dynamics within Solanaceae.
We hope our work serves as an example of how phylogenetic comparative methods can be used to disentangle the contributions of interacting traits to heterogeneous lineage diversification, and how to statistically argue for increasing complexity in diversification modeling.

@@

%R- let's not get into the weeds of what is a hidden state (I remove the use of trait  for state because a state is what the model receives). Jeremy does a good job discussing this in his paper so no need.
%     but don't be circular, test in different clade
% alpha is always low: new supp fig showing how A & B are inferred on the tree?  at least for ID/CD/CP+A/B model - it is low because not enough transitions and mostly a different process towards the tips-who knows what is happening there?
%Here Rosana adds the value of adding traits with the lumped models
As more trait information becomes available for macroevolutionary studies, it is not only important to recognize the role of hidden states as a part of a general modeling approach, but also to question whether adding more traits to diversification studies is justified.  More generally, we find that lumped models are useful for assessing the value of adding additional traits to already complex diversification models(\cref{figure:lumped,table:lumped}).
%R-removed this: %In our analyses, we find that the transition rates between and within hidden traits did not affect the direction of the net diversification differences. 
%We find that it is important to allow for the hidden state transition rates to be asymmetrical, because those models tend to provide a better fit than models that fix the hidden state transition rates to be equal (\cref{suppfigure:asymmetric,supptable:asymmetry}).

Although we fit an extensive set of models in order to relax a variety of assumptions, we did not explore the process of trait change in conjunction with speciation.
That is, our models all assume anagenetic trait evolution and ignore cladogenetic shifts.
Anagenetic and cladogenetic changes can be separated with phylogenetic models \citep{mayrose_2011, goldberg_2012, magnuson-ford_2012}. 
These have been applied to estimate the relative contribution of anagenetic and cladogenetic shifts in breeding system \citep{goldberg_2012} and polyploidization \citep{zhan_2016, freyman_2019}.
We did not explore cladogenetic trait change because they would greatly increase in state space and model number of our already complex and extensive modeling framework. %IM: #29 and GB suggested that chance
Although \citet{goldberg_2012} found that allowing cladogenetic changes did not substantially affect inference of net diversification rates associated with breeding system, future work could test whether this process affects diversification rate estimates with the more complex state and parameter spaces of our other models.

@@

With evolution predominantly in the direction from diploid to polyploid, and from SI to SC, surviving lineages will tend to become SC polyploids.
We find that in Solanaceae, the pathway to this state is more likely to consist of a single step ($ID \rightarrow CP$) than two steps ($ID \rightarrow CD \rightarrow CP$; \cref{figure:pathways}).
Although this question focuses on the process of state transitions, we also show that its answer is affected by the process of lineage diversification.
We used a simple mathematical approach to investigate the contributions of the two pathways, but future work could instead rely on stochastic character mapping to estimate the numbers of each type of transition more directly.

@@

Our findings prompt several further questions about the macroevolutionary pathways of ploidy and breeding system.
%
First, our support for the direct pathway is consistent with the idea that breakdown of SI by whole genome duplication---via diploid `heteroallelic' pollen---may trigger the evolution of gender dimorphism as a different mechanism of inbreeding avoidance \citep{miller_2000}.
A further test of this hypothesis would additionally examine the propensity of polyploids generated through either pathway to become dioecious \citep{robertson_2011}.
Second, we might wonder whether the propensity for a polyploid species to diversify depends on whether it arose via the one-step or two-step pathway.
This could be tested with a different form of a hidden state model, in which the polyploid state is subdivided into parts, reflecting the arriving path taken to that state. %IM: #30 and GB 
Such an estimate of path-dependence could also include the possibility of different diversification rates for the subdivided $CP$ substates.
Third, the generality of our findings in other families remains to be assessed.
An identical procedure could be used in other families with gametophytic SI.
In clades with sporophytic SI systems, however, SI is not disabled by whole genome duplication, so there is no one-step pathway \citep{miller_2000,mable_2004}.
The correlation between breeding system and ploidy may therefore be different in sporophytic systems, and it is unclear whether one of the two-step pathways might predominate.
% pathways: compare/contrast with robertson2011
%     \rho_I > \rho_C in all!
%     likely way to lose SI
%     likely way to become P

### 2019-07-18 manuscript/introduction.tex
All co-authors input added, figures corrected

Polyploidization is a remarkably common mutation in plants \citep{husband_2013, zenilferguson_2017}.
The widespread prevalence of variation in ploidy has long been considered a salient feature of flowering plant lineages \citep{stebbins1938}. 
Increase in ploidy can alter many traits and affect a variety of evolutionary and ecological processes \citep{ramsey_2002, sessa_2019}.
Polyploids were found to have an overall lower net diversification rate than diploids across many vascular plant clades \citep{mayrose_2011, mayrose_2015}. 
However, recent genomic studies have inferred numerous paleo-polyploidizations, including some preceding the emergence of highly diverse plant clades \citep{soltis_2014, landis_2018}, suggesting that whole genome duplications may have played an important macroevolutionary role driving innovation and diversification in plants. 
Evidence of paleo-polyploidy within the genomes of diploid extant plants also implies pervasive diploidization, the return of polyploids to the diploid state, throughout the angiosperm phylogeny \citep{soltis_2015, dodsworth_2015}.
Our analyses re-examine the association between ploidy and lineage diversification by extending the approach of \citet{mayrose_2011, mayrose_2015} to include transitions from polyploid to diploid states and potential unobserved factors affecting diversification patterns.

Breeding system shifts---changes in the collection of physiological and morphological traits that determine the likelihood that any two gametes unite---are also remarkably common and crucially affect the distribution and amount of genetic variation in populations \citep{barrett2013}. 
In particular, a variety of genetic self-incompatibility (SI) systems cause plants to reject their own pollen, and loss of such mechanisms, yielding self-compatibility (SC), is one of the most replicated transitions in flowering plant evolution \citep{stebbins1974, igic_2008}.
Previous analyses reported higher rates of diversification for SI than for SC lineages in Solanaceae \citep{goldberg_2010}. 
Similarly, heterostylous SI lineages in Primulaceae seem to diversify faster \citep{devos2014}, as do outcrossing lineages in Onagraceae \citep{freyman_2019}.
Although these findings suggest a consistent macroevolutionary role of breeding system, it is unlikely to be the sole character determining lineage diversification.
We investigate the relationship of breeding system to speciation and extinction rates in the context of ploidy and other unobserved factors.

Polyploidy and self-fertilization are widely thought to be associated \citep{stebbins1950}.
There are several possible general explanations: whole genome duplication may facilitate the transition to selfing by masking inbreeding depression, self-fertilization may facilitate polyploidy establishment by avoiding the triploid bridge, or both selfing and polyploidy may tend to be found in weedy or peripheral populations \citep{ramsey_1998, barringer2007, barrett2008, husband2008}.
Additionally, in RNase-based gametophytic SI systems, polyploidization directly causes the loss of SI \citep{stout1942, lewis1947}.
%B: disclaimer: ceteris paribus statement omitted; polyploidization ordinarily causes SC because of the formation of heterodiploid pollen. On the background of deletion of S-locus, or with heterologous chromosome homozygosity at the S-locus may not do so. These, however, appear to be sufficiently rare that they are recovered perhaps twice in dicots: once (or twice) naturally, in sour cherry and its close relative (Prunus), and once in a experimentally induced and selected synthetic pentaploid Solanum (which has not been replicated). Strictly speaking, this is a feature of non-self recognition systems of the kind found in RNase-based GSI.
In these systems, SI occurs because haploid self-pollen grains, with one S-allele at the locus controlling the SI response, are unable to detoxify the S-RNase produced by the same S-allele in the style \citep{kubo2010}.
The unreduced pollen of diploids, however, can contain two S-alleles expressed in pollen, which jointly gain the ability to detoxify the S-RNases produced by any maternal genotype \citep{entani1999, tsukamoto2005, kubo2010}.
Initial mutant individuals with pollen containing doubled haploid genomes are consequently capable of self-fertilization, with exceedingly few exceptions \citep{hauck_2002, nunes_2006}.
RNase-based SI is regarded as ancestral in eudicots \citep{igic_2001,steinbachs_2002}, and it is expressed in all SI species of Solanaceae examined to date.
The consequent absence of SI polyploids in this family yields a strong correlation between ploidy and breeding system \citep{robertson_2011}.

We address two macroevolutionary questions about the correlated evolution of ploidy and breeding system.
First, we investigate their joint influence on rates of speciation and extinction.
Each character alone has been shown to associate with differential lineage diversification, but if their effects are not additive, studying them separately may not reveal the effects of their combinations.
Second, we examine the order of transitions in the two characters.
Evolution commonly proceeds from diploid to polyploid, and from SI to SC states, but there are two paths by which diploid SI lineages can eventually become SC polyploids.
Loss of SI in diploids could be directly caused by polyploidization (as explained above, for RNase-based SI systems), resulting in a one-step pathway to SC polyploids. 
Alternatively, SI diploids could first transition to SC without an increase in ploidy, and subsequently undergo polyploidization, resulting in a two-step pathway to SC polyploids.
\citet{robertson_2011} compared the contributions of these two paths, finding that evolution from SI diploids to SC polyploids is more likely to proceed via the one-step pathway over short timescales, but via the two-step pathway over long timescales.
They considered only transitions among the states, however, and we investigate whether these results hold true when allowing for differences in lineage diversification.

In the present study, we employ an extended framework of state speciation and extinction models, which simultaneously model transitions between the discrete states of a trait and different rates of speciation and extinction associated with each of those states \citep[`SSE' models;][]{maddison_2007, fitzjohn_2012}.
We start by fitting binary state speciation and extinction models to each ploidy and breeding system independently \citep{maddison_2007}.
We follow by fitting models that incorporate hidden states, which reduce the chance that an effect of one trait on diversification would be mistaken for the effect of an unobserved factor \citep{beaulieu_2016}.
We compare the proposed models against their character independent counterparts \citep{beaulieu_2016} to investigate whether ploidy or breeding system are actually informative of the diversification process.
Next, we model ploidy and breeding system jointly to assess their combined influence on diversification, with or without an additional hidden character.
Using the ploidy and breeding system model without hidden states, we quantify the relative contributions of the two pathways from SI diploids to SC polyploids.
We also aggregate states within these joint models of ploidy and breeding system in order to test whether increasing complexity from one trait to two traits significantly improves our understanding of the diversification process.
Furthermore, we extend all the models involving ploidy to investigate the potential effects of including diploidization.
% And finally, we explore models of diversification using asymmetric rates between and within hidden states to investigate the sensitivity of the statistical inference to model assumptions.
Our results highlight the importance of considering non-additive effects of traits on net diversification rates  under the presence of unobserved factors, in order to detect strong biologically-driven processes dictating the diversification patterns.

>>>>

Polyploidization is a remarkably common mutation in plants \citep{husband_2013, zenilferguson_2017}.
The widespread variation in ploidy has long been considered a salient feature of flowering plant lineages \citep{stebbins1938}. 
An increase in ploidy can alter many traits and affect a variety of evolutionary and ecological processes \citep{ramsey_2002, sessa_2019}.
At shallow evolutionary time scale, polyploids were found to have an overall lower net diversification rate than diploids across many vascular plant clades \citep{mayrose_2011, mayrose_2015}. %IM suggestion
However, recent genomic studies have inferred numerous paleo-polyploidizations, including some preceding the emergence of highly diverse plant clades \citep{soltis_2014, landis_2018}, suggesting that whole genome duplications may have played an important  role driving innovation and diversification in plants. 
Evidence of paleo-polyploidy within the genomes of diploid extant plants also implies pervasive diploidization, the return of polyploids to the diploid state, throughout the angiosperm phylogeny \citep{soltis_2015, dodsworth_2015}.
Our analyses re-examine the association between ploidy and lineage diversification by extending the approach of \citet{mayrose_2011, mayrose_2015} to include transitions from polyploid to diploid states and potential unobserved factors affecting diversification patterns.

Breeding system shifts---changes in the collection of physiological and morphological traits that determine the likelihood that any two gametes unite---are also remarkably common and crucially affect the distribution and amount of genetic variation in populations \citep{barrett2013}. 
In particular, a variety of genetic self-incompatibility (SI) systems cause plants to reject their own pollen, and the loss of such mechanisms, yielding self-compatibility (SC), is a commonly observed transition in flowering plant evolution \citep{stebbins1974, igic_2008}.
Previous analyses reported higher rates of diversification for SI than for SC lineages in Solanaceae \citep{goldberg_2010}. 
Similarly, heterostylous SI lineages in Primulaceae seem to diversify faster than SC lineages \citep{devos2014}, as do outcrossing lineages in Onagraceae \citep{freyman_2019}.
Although these findings suggest a consistent macroevolutionary role of breeding system, it is unlikely to be the sole character determining lineage diversification.
We investigate the relationship of breeding system to speciation and extinction rates in the context of ploidy and other unobserved factors.

Polyploidy and self-fertilization are widely thought to be associated \citep{stebbins1950}.
Whole genome duplication may facilitate the transition to selfing by masking inbreeding depression, or self-fertilization may facilitate polyploidy establishment by by avoiding the lower fitness that characterize early-forming polyploids \citep{levin_1975,ramsey_1998, barringer2007, barrett2008, husband2008}.%IM suggestion and Gordon suggestion
Additionally, in RNase-based gametophytic SI systems, polyploidization directly causes the loss of SI \citep{stout1942, lewis1947}.
%B: disclaimer: ceteris paribus statement omitted; polyploidization ordinarily causes SC because of the formation of heterodiploid pollen. On the background of deletion of S-locus, or with heterologous chromosome homozygosity at the S-locus may not do so. These, however, appear to be sufficiently rare that they are recovered perhaps twice in dicots: once (or twice) naturally, in sour cherry and its close relative (Prunus), and once in a experimentally induced and selected synthetic pentaploid Solanum (which has not been replicated). Strictly speaking, this is a feature of non-self recognition systems of the kind found in RNase-based GSI.
In these systems, SI occurs because haploid self-pollen grains, with one S-allele at the locus controlling the SI response, are unable to detoxify the S-RNase produced by the same S-allele in the style \citep{kubo2010}.
The unreduced pollen of diploids, however, can contain two S-alleles expressed in pollen, which jointly gain the ability to detoxify the S-RNases produced by any maternal genotype \citep{entani1999, tsukamoto2005, kubo2010}.
Initial mutant individuals with pollen containing doubled haploid genomes are consequently capable of self-fertilization, with exceedingly few exceptions \citep{hauck_2002, nunes_2006}.
RNase-based SI is regarded as ancestral in eudicots \citep{igic_2001,steinbachs_2002}, and it is expressed in all SI species of Solanaceae examined to date.
The absence of SI polyploids in this family yields a strong correlation between ploidy and breeding system \citep{robertson_2011}.

We address two macroevolutionary questions about the correlated evolution of ploidy and breeding system.
First, we investigate their joint influence on rates of speciation and extinction.
Each character alone has been shown to be associated with differential lineage diversification, but if their effects are not additive, studying them separately may not reveal their combined effect.
Second, we examine the order of transitions in the two characters.
Evolution commonly proceeds from diploid to polyploid, and from SI to SC states, but there are two paths by which diploid SI lineages can eventually become SC polyploids.
Loss of SI in diploids could be directly caused by polyploidization (as explained above, for RNase-based SI systems), resulting in a one-step pathway to SC polyploids. 
Alternatively, SI diploids could first transition to SC without an increase in ploidy, and subsequently undergo polyploidization, resulting in a two-step pathway to SC polyploids.
\citet{robertson_2011} compared the contributions of these two paths, finding that evolution from SI diploids to SC polyploids is more likely to proceed via the one-step pathway over short timescales, but via the two-step pathway over long timescales.
They considered only transitions among the states, however, and we investigate whether these results hold true when allowing for differences in lineage diversification.

In the present study, we employ an extended framework of state speciation and extinction models, which simultaneously model transitions between the discrete states of a trait and different rates of speciation and extinction associated with each of those states \citep[`SSE' models;][]{maddison_2007, fitzjohn_2012}.
We start by fitting binary state speciation and extinction models to ploidy and breeding system independently \citep{maddison_2007}.
We follow by fitting models that incorporate hidden states, which reduce the chance that the effect of the focal trait (ploidy or breeding system) on diversification is found to be significant when in reality, it is simply background heterogeneity in the diversification process what produces the diversification patterns in the phylogeny \citep{beaulieu_2016}. %IM: added a little more explanation
We compare the proposed models against their character independent counterparts \citep{beaulieu_2016} to investigate whether ploidy or breeding system are actually affect the diversification process.
Next, we model ploidy and breeding system jointly to assess their combined influence on diversification, with or without an additional hidden state.
Using the ploidy and breeding system model without hidden states, we quantify the relative contributions of the two pathways from SI diploids to SC polyploids.
We also aggregate states within these joint models of ploidy and breeding system in order to test whether increasing complexity from one trait to two traits significantly improves our understanding of the diversification process.
Furthermore, we extend all the models involving ploidy to investigate the potential effects of including diploidization.
% And finally, we explore models of diversification using asymmetric rates between and within hidden states to investigate the sensitivity of the statistical inference to model assumptions.
Our results highlight the importance of considering non-additive effects of traits on net diversification rates  under the presence of unobserved factors, in order to detect strong biologically-driven processes dictating the diversification patterns.

### 2019-07-18 manuscript/main.tex
All co-authors input added, figures corrected

%--------------------------------------------------
\section{Acknowledgements}
%--------------------------------------------------
Special thanks to Bob Thomson for donating computational resources that made possible testing the convergence of the models. 
We also thank Sergei Tarasov for clarifying lumpability concepts, and Carrie Tribble for troubleshooting some ancestral estimate figures. 
The computing resources were provided by the Minnesota Supercomputing Institute (MSI) at the University of Minnesota.
This work was supported by the National Science Foundation grant DEB-1655478 (to EEG), DEB-1655692 and NESCent sabbatical scholar award EF-0905606 (to BI), and the Israel Science Foundation 961/17 (to IM). %IM: #32
%B: new:
We thank Dan Schoen and three anonymous reviewers for providing uncommonly thoughtful and helpful reviews, as well as Spencer Barrett for continually inspiring our work.

>>>>

%--------------------------------------------------
\section{Acknowledgements}
%--------------------------------------------------
Special thanks to Bob Thomson for donating computational resources that made possible testing the convergence of the models. 
We also thank Sergei Tarasov for clarifying lumpability concepts, and Carrie Tribble for troubleshooting some ancestral estimate figures. 
The computing resources were provided by the Minnesota Supercomputing Institute (MSI) at the University of Minnesota.
This work was supported by the National Science Foundation grant DEB-1655478 (to EEG and IM), DEB-1655692 and NESCent sabbatical scholar award EF-0905606 (to BI), and the Israel Science Foundation 961/17 (to IM). %IM: #32
%B: new:
We thank Dan Schoen and three anonymous reviewers for providing uncommonly thoughtful and helpful reviews, as well as Spencer Barrett for continually inspiring our work.
